---
title: "tutorial2"
output: html_document
date: "2026-10-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# First title
## Sub title
I know how markdown works, I just want to test the PDF thing.

```{r}
library(tidyverse)
videos <- read.csv("video_view.csv")
```

```{r}
getwd()
list.files()
```
# Actual programming stuff
Let's first inspect the data
```{r}
library(dplyr)
head(videos)
glimpse(videos)
names(videos)
```
Extra practice tutorial 1
```{r}
creators <- videos %>% summarize(
  impressions_total = sum(impressions_n, na.rm = TRUE),
  avg_watch_rate = mean(watch_rate, na.rm = TRUE),
  .by = creator_id
)
creators <- creators %>% arrange(desc(impressions_total))
```

Okay nu weer verder met tutorial 2

Which videos are both high quality and reasonably visible?
Predict first: If we require watch_rate >= 0.7 and impressions_n >= 20, do we keep many or few
rows?

```{r}
best_videos <- videos %>% select(video_id, creator_id, watch_rate, impressions_n) %>% filter(watch_rate >= 0.7 & impressions_n >= 20)

nrow(videos)
nrow(best_videos)
nrow(best_videosnrow(videos) - nrow(best_videos)
```
Question:
How can we create and rank a simple video performance score?
Predict first:
Will watched_n / impressions_n likely be close to watch_rate?
Plan:
1. create new variable watched_share
2. rename long variable names for readability
3. sort descending to see top rows first
```{r}
videos %>% summarise( total_impressions = sum(impressions_n, na.rm = TRUE), avg_watch_rate = mean(watch_rate, na.rm = TRUE), n_videos = n())
```
Create object top_watch, that contains the following information: the video id, creator id, watch
rate, and at least 50 impressions per video. Arrange your answer by having watch rate, descending
```{r}
top_watch <- videos %>% mutate(watch_rate_new = watched_n/impressions_n) %>% filter(impressions_n > 50) %>% 
  select(video_id, creator_id, watch_rate) %>% arrange(desc(watch_rate))
```

Extra practice questions
1. Count videos with watch_rate >= 0.8.
3. Find creators with at least 3 videos and sort by total impressions.
4. Create a short interpretation paragraph (3 lines) for your creator_summary.
5. Add a section to README called “Troubleshooting” with 3 common errors.
6. Render your Quarto file again after one small text edit and verify output updates

```{r}
high_watch_rate <- videos %>% filter(watch_rate >= 0.8)
nrow(high_watch_rate)
```
```{r}

```














